### 2016-01-18 paper.tex
Remove first sentence of turbine model section

% For figure citations, please use "Fig." instead of "Figure".

A 1:6 scale physical model of the RM2 rotor was designed and fabricated. Turbine
geometric parameters were scaled from the RM2 design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
model \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

>>>>

Geometric parameters for the 1:6 scale RM2 rotor were taken from the RM2 design
report \cite{Barone2011}, with the exception of the shaft diameter, which was
scaled from the SAFL RM2 model \cite{Hill2014}. The hubs were designed to be
similar to the SAFL model, which may aid in comparison of the results, though
this was not a top priority. Geometric parameters are shown in
Tab.~\ref{tab:turb-geom} and a drawing of the turbine design is shown in
Fig.~\ref{fig:turbine-drawing}. The turbine model components---blades, struts,
shaft, and center hub sections---were fabricated from 6061-T6 aluminum, which
was hardcoat anodized per MIL-8625-A, type III, class 2 specifications. CAD
models of the turbine are available from \cite{Bachant2015-RM2-CAD}.
